---
title: "Beginning Data Science"
author: "Jarrett Glass"
format: html
editor: visual
---

## 1. What do you think being a data scientist is about?

Being a Data Scientist is about taking information - data, of course - and finding ways to record, clean, and manipulate it in order to extrapolate other useable details. 

## 2. What differences/similarities do you see between data scientists and statisticians?

I see some similarities where:

* Both can work with either supervised or unsupervised data.

* Both may generate models to describe a current (or past) event, and use said model to try to determine what may happen in the future.

Some differences may be that

* Statisticians would need data to be cleaned, while data scientists may perform work even on uncleaned (dirty?) data.

* Statisticians would also more be more likely to use smaller datasets, while data scientists may turn to larger, broader data sets.

## 3. How do you view yourself in relation to these two areas?

I have been studying statistics for several years now, but foresee my career taking me more into the "data scientist" realm. I am considering a foray into biostatistics, and from there, possibly into a bioinformaticist role (or a blend of bioinformatics and data science).

---

Next, there will be some code performed on a component of the `iris` dataset.

```{r}
y <- density(iris$Petal.Width)

# The Class of the object 'y'
class(y)
# The Type of the object 'y'
typeof(y)
# The structure of the object 'y'
str(y)
```

Next, I will write another R code chunk, to use the `plot` function on `y`. The code will be hidden by setting `#| echo: false` inside the code block.

```{r}
#| echo: false

plot(y)
```

Thus concludes the requirements of this document for the assignment!